Computationally Efficient High-Dimensional Regularized Discriminant Analysis

### 2017-01-21 reports/paper-hdrda.Rnw
Updated paper's title

\title{High-Dimensional Regularized Discriminant Analysis}

@@

<<knitr_setup, include=FALSE, echo=FALSE, cache=FALSE>>=
# Round digits throughout document including \Sexpr statements.
# See Yihui's response here:
# http://stackoverflow.com/questions/11062497/how-to-avoid-using-round-in-every-sexpr
options(digits=3)

>>>>

\title{Computationally Efficient High-Dimensional Regularized Discriminant Analysis}

@@

<<knitr_setup, include=FALSE, echo=FALSE, cache=FALSE>>=
library(knitr)
# Round digits throughout document including \Sexpr statements.
# See Yihui's response here:
# http://stackoverflow.com/questions/11062497/how-to-avoid-using-round-in-every-sexpr
options(digits=3)
